% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jiashuo Yu}

\basicInfo{
    \email{joshuayu.2048@gmail.com} \textperiodcentered\ 
    \phone{(+86) 138-5023-6448} \textperiodcentered\ 
    \github{https://github.com/hairendezi}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Fuzhou University (FZU)}, Fuzhou, China}{2023 -- Present}
\textit{Master student} in Computer Science and Technology (CS), expected June 2026
\datedsubsection{\textbf{Fuzhou University (FZU)}, Fuzhou, China. GPA: 3.745 (4/52)}{2019 -- 2023}
\textit{B.S.} in Computer Science and Technology (CS)

\section{\faBook\ Publications}
\begin{itemize}[parsep=0.5ex]
    \item \textbf{Jiashuo Yu}, Long Huang, Longlong Zhu, Dong Zhang, Chunming Wu. DTRadar: Accelerating Search Process of Decision Trees in Packet Classification. IEEE ISCC 2023 (CCF C).
    \item Longlong Zhu, \textbf{Jiashuo Yu}, Long Huang, Linying Zheng, Jinfeng Pan, Zhengyan Zhou, Hanze Chen, Dong Zhang, Xiang Chen, Chunming Wu. MiCuts: Combing Bit-based Cutting and Splitting for Efficient Packet Classification. IEEE ICC 2023 (CCF C)
    \item Jiayi Cai, Zhengyan Zhou, Tingxin Sun, \textbf{Jiashuo Yu}, Longlong Zhu, Zizhao Wang, Chengze Li, Dong Zhang, Chunming Wu. MINT: Empowering Multiple Flow Definition Query for Network-wide Measurement. IEEE ICC 2023 (CCF C)
    \item Longlong Zhu, \textbf{Jiashuo Yu}, Jiayi Cai, Jinfeng Pan, Zhigao Li, Zhengyan Zhou, Dong Zhang, Chunming Wu. FROD: An Efficient Framework for Optimizing Decision Trees in Packet Classification. IEEE IWQoS 2022 (CCF B)
\end{itemize}

\section{\faHeartO\ Selected Awards}
\datedline{The 13th Service Outsourcing Innovation and Entrepreneurship Competition, Second Prize}{Jul. 2022}
\datedline{The 6-th National Future Network Technology Innovation Competition, Third Prize}{Aug. 2022}
\datedline{2021 C4-Network Technology Challenge, Second Prize}{Oct. 2021}
\datedline{The 2021 Merit Student, Fuzhou University}{May. 2021}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: 
\end{itemize}



\end{document}